---
title: "Cleaning ALA data to Final Data - Arid & Mesic"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: inline
---
Installing packages
```{r}
library(writexl)
library(dplyr)
```
Reading in mesic and arid species data downloaded from Atlas of Living Australia
```{r}
Mesic_data <- read.csv("Final_Mesic.csv")
Arid_data <-read.csv("Final_Arid.csv")
```
Filtering out data with uncertainity >3001, no year, species name, latitude or longitude values
```{r}
Mesic_data <- Mesic_data %>%
  filter(!is.na(year) & !is.na(species) & !is.na(decimalLatitude) & !is.na(decimalLongitude)) %>% #excluding data points without a year, species, coordinates
  filter(coordinateUncertaintyInMeters <= 3001) %>% mutate(abs_lat=abs(decimalLatitude)) %>%
  mutate(abs_lon=abs(decimalLongitude))

Arid_data <- Arid_data %>%
  filter(!is.na(year) & !is.na(Species) & !is.na(decimalLatitude) & !is.na(decimalLongitude)) %>% #excluding data points without a year, species, coordinates
  filter(coordinateUncertaintyInMeters <= 3001) %>% mutate(abs_lat=abs(decimalLatitude)) %>%
  mutate(abs_lon=abs(decimalLongitude))
```
Adding columns for min and max latitude and longitude and filtering out species that exist beyond the latitudinal and longitudinal boundaries
```{r}
filtered_mesic = Mesic_data %>% group_by(species) %>%
  summarise(max_lat=max(abs_lat),
            min_lat=min(abs_lat),
            max_lon=max(abs_lon),
            min_lon=min(abs_lon)) %>% dplyr::filter(min_lat >= 19.21 &  max_lat <= 31.66 & min_lon >= 147.46 &  max_lon <= 153.94)

filtered_arid = Arid_data %>% group_by(Species) %>%
  summarise(max_lat=max(abs_lat),
            min_lat=min(abs_lat),
            max_lon=max(abs_lon),
            min_lon=min(abs_lon)) %>% dplyr::filter(min_lat >= 19.21 &  max_lat <= 31.66 & min_lon >= 115.62 &  max_lon <= 143.15)

```
Creating csv of species list data
```{r}
write_xlsx(filtered_mesic, "/Users/Euan/Desktop/Honours/Historic data/Final_Mesic_List.csv")

write_xlsx(filtered_arid, "/Users/Euan/Desktop/Honours/Historic data/Final_Arid_List.csv")
```