#When did climate change begin? A climate analysis:
uploading all required packages:
```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)
library(broom)
library(ggforce)
library(tidyr)
library(ggtext)
install.packages("skimr")
library(skimr)
library(purrr)
install.packages("patchwork")
library(patchwork)
library(mgcv) #For GAM function
install.packages("egg")
library(egg)
install.packages("gratia")
library(gratia) #testing GAMs
install.packages("strucchange")
library(strucchange)#For breakpoints analysis
install.packages("utils")
library(utils)
install.packages("WRS2")
library(WRS2)
install.packages("scales")
install.packages("segmented")
library(segmented)
library(scales)
```
Uploade arid and mesic data:
```{r}
setwd("~/Desktop/Honours/Historic data")

arid_temp_data <- read.csv("Alice_Springs_Max_Temp_Data.csv", stringsAsFactors=FALSE, fileEncoding="latin1")

mesic_temp_data <-read.csv("Amberley_Max_Temp_Data.csv", stringsAsFactors=FALSE, fileEncoding="latin1")
```
Calculate average annual temperature for the arid polygon
```{r}
arid_year_temp <- arid_temp_data %>% # Some data wrangling to get study duration
  group_by(Year) %>%
  summarize(
    MaxTemp = max(max_temp, na.rm=T),
    averageTemp = mean(max_temp, na.rm=T)
      )
arid_year_temp <- subset(arid_year_temp, Year>1940) # Because the records weren't full for 1941 the temperature appears hotter than the annual average and thus I'm removing it
```
Calculate average annual temperature for the mesic polygon
```{r}
mesic_year_temp <- mesic_temp_data %>% # Some data wrangling to get study duration
  group_by(Year) %>%
  summarize(
    MaxTemp = max(max_temp, na.rm=T),
    averageTemp = mean(max_temp, na.rm=T)
      )
mesic_year_temp <- subset(mesic_year_temp, Year>1940) # Because the records weren't full for 1941 the temperature appears hotter than the annual average and thus I'm removing it
```
Arid segmented/breakpoints regression:
```{r}
arid_seg_lm <- lm(averageTemp ~ Year, data = arid_year_temp)
arid_seg_temp <-segmented(arid_seg_lm)
summary(arid_seg_temp)

#suggesting that the initial heating has been recorded around 2019 (+ or - 1 year)
```
Mesic segmented/breakpoints regression:
```{r}
mesic_seg_lm <- lm(averageTemp ~ Year, data = mesic_year_temp)
mesic_seg_temp <-segmented(mesic_seg_lm)
summary(mesic_seg_temp)

#suggesting that the initial heating has been recorded around 1976 (+ or - 7 year)
```
Arid plot
```{r}
plot(arid_year_temp$Year, arid_year_temp$averageTemp, pch=16, col ='steelblue', ylab = "Average annual temperature", xlab = "Year", cex.lab = 3, cex= 1.2, cex.lab = 1.2)
plot(arid_seg_temp, add=T)
```
```{r}
arid_bp_temp1 <-breakpoints(averageTemp ~ Year, data = arid_year_temp)
summary(arid_bp_temp1) #suggesting a breakpoint around 1953
```
Mesic plot
```{r}
plot(mesic_year_temp$Year, mesic_year_temp$averageTemp, pch=16, col ='steelblue', ylab = "Average annual temperature", xlab = "Year", cex.lab = 3, cex= 1.2, cex.lab = 1.2)
plot(mesic_seg_temp, add=T)
```
```{r}
mesic_bp_temp1 <-breakpoints(averageTemp ~ Year, data = mesic_year_temp)
summary(mesic_bp_temp1) #suggesting a breakpoint around 1953
```
A GAM analysis: Arid
```{r}
arid_temp_gam <- gam(averageTemp ~ s(Year, k=70), data = arid_year_temp, method = "REML")
summary(arid_temp_gam)
gam.check(arid_temp_gam, rep=500)
appraise(arid_temp_gam)
```
Arid - analysis presents a similar trend of increase in warming around the mid 1970's
```{r}
arid_p_temp <- ggplot(arid_year_temp, aes(Year, averageTemp)) +
  geom_point() +
  geom_smooth(method = "gam", formula = y ~ s(x, k=70), aes(color = "gam", fill = "confidence interval"))+
  scale_fill_manual(values = "lightblue", name = NULL) +
  scale_color_manual(values = "darkblue", name = NULL) +
  theme_article()
arid_p_temp
```