Load packages
```{r}
library(ggplot2)
library(dplyr)
library(gridExtra)
```
Import datasets
```{r}
Arid_Species <- read.csv("Final_Arid.csv")
Mesic_Species <- read.csv("Final_Mesic.csv")
```
Load Latitude data for Arid species
```{r}
species_list <- unique(Arid_Species$Species) #Create a list of arid species

i = 1 #Run the first species in the list manually to troubleshoot

species_list[i] 

df_temp <- Arid_Species %>% filter(Species == species_list[i]) #DataFrame filtered by the study species
  lm_temp <- lm(decimalLatitude ~ year, data = df_temp) #Run the linear model
  summary_temp <- summary(lm_temp) #Save the summary stats
  p_temp <- pf(summary_temp$fstatistic[1], #Calculating the p-value from the three f statistics
               summary_temp$fstatistic[2],
               summary_temp$fstatistic[3],lower.tail=F)

  summary_temp

  stats_temp <- data.frame( #make a table of summary statistics:
    species = species_list[i], #assign species 1 to species list
    formula = "lm(decimalLatitude ~ year)",
    n = nrow(df_temp), #number of records
    year_effect = lm_temp[["coefficients"]][["year"]], #effect of year slope
      year_se = summary_temp[["coefficients"]][["year","Std. Error"]], #standard error of the slope
    r_sq = summary_temp[["r.squared"]], #r squared
    r_squ_adj = summary_temp[["adj.r.squared"]], #adjusted r squared
    p_val = p_temp, #obtain the p-value
    sig = p_temp < 0.05 #determine whether the p-value significant
    )
  
  summary_stats_1 <- stats_temp 
  
  summary_stats_2 <- stats_temp

   rm(i, df_temp, lm_temp, summary_temp, p_temp, stats_temp) #removed temporary data now that everything is on the summary table

```
Creating latitude graph for Arid species 1-40
```{r}
summary_stats_1<-c()

for (i in 1:40) { #loop for species 1 to 40 (Acaica abrupta - Eremophila metallicorum)

df_temp <- Arid_Species %>% filter(Species == species_list[i]) 
  lm_temp <- lm(decimalLatitude ~ year, data = df_temp) 
  summary_temp <- summary(lm_temp)
    p_temp <- pf(summary_temp$fstatistic[1], 
               summary_temp$fstatistic[2],
               summary_temp$fstatistic[3],lower.tail=F)
  stats_temp <- data.frame( 
    species = species_list[i], 
    formula = "lm(decimalLatitude ~ year)", 
    n = nrow(df_temp), 
    year_effect = lm_temp[["coefficients"]][["year"]], 
    year_se = summary_temp[["coefficients"]][["year","Std. Error"]], 
    r_sq = summary_temp[["r.squared"]], 
    r_squ_adj = summary_temp[["adj.r.squared"]], 
    p_val = p_temp,
    sig = p_temp < 0.05 
    )

  summary_stats_1 <- bind_rows(summary_stats_1, stats_temp) #attach the new data onto the summary table
  
   rm(df_temp, lm_temp, summary_temp, p_temp, stats_temp)
}

summary_stats_1 #have a look at the summary table to ensure columns and rows are correct

cbPalette <- c("#999999", "#000000") #create blue (mesic) and orange (arid) colour scheme

#Create plot of latitude shifts of arid species 1-40
LatArid1to40 <- ggplot(data = summary_stats_1, aes(year_effect, species,color=sig))+
  geom_point()+ scale_colour_manual(values = cbPalette) +
  xlab("Mean Rate of Latitude Shift (degrees/year)")+
  ylab("Arid Species") +
  geom_errorbar(aes(xmin=year_effect-year_se, xmax=year_effect+year_se))+
  theme_classic()+
  scale_x_continuous(breaks = seq(-0.08,0.12, 0.04), limits = c(-0.08,0.12))+
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        axis.text.y = element_text(face="italic")) +
  theme(text = element_text(size = 13)) + 
  geom_line() +
  geom_vline(xintercept = 0, colour = "red", linetype= "dashed") 

LatArid1to40 #view plot

ggsave("LatArid1to40.pdf", plot = LatArid1to40, height = 6, width = 6, dpi = 300)

```
Creating latitude graph for Arid species 41-80
```{r}
summary_stats_2<-c()

for (i in 41:80) { #loop for species 41 to 80 (Eremophila neglecta - Xerochrysum interiore)

df_temp <- Arid_Species %>% filter(Species == species_list[i]) 
  lm_temp <- lm(decimalLatitude ~ year, data = df_temp) 
  summary_temp <- summary(lm_temp) 
    p_temp <- pf(summary_temp$fstatistic[1], 
               summary_temp$fstatistic[2],
               summary_temp$fstatistic[3],lower.tail=F)

  stats_temp <- data.frame( 
    species = species_list[i], 
    formula = "lm(decimalLatitude ~ year)", 
    n = nrow(df_temp), #number of records
    year_effect = lm_temp[["coefficients"]][["year"]], 
    year_se = summary_temp[["coefficients"]][["year","Std. Error"]], 
    r_sq = summary_temp[["r.squared"]],
    r_squ_adj = summary_temp[["adj.r.squared"]], 
    p_val = p_temp,
    sig = p_temp < 0.05 
    )
  
  summary_stats_2 <- bind_rows(summary_stats_2, stats_temp)

   rm(df_temp, lm_temp, summary_temp, p_temp, stats_temp) 
}

summary_stats_2 

#Create plot of longitude shifts of arid species 1-40
LatArid41to80 <- ggplot(data = summary_stats_2, aes(year_effect, species,color=sig))+
  geom_point()+ scale_colour_manual(values = cbPalette) +
  xlab("Mean Rate of Latitude Shift (degrees/year)")+
  ylab("Arid Species") +
  geom_errorbar(aes(xmin=year_effect-year_se, xmax=year_effect+year_se))+
  theme_classic()+
  scale_x_continuous(breaks = seq(-0.08,0.12, 0.04), limits = c(-0.08,0.12))+
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        axis.text.y = element_text(face="italic")) +
  theme(text = element_text(size = 13)) + 
  geom_line() +
  geom_vline(xintercept = 0, colour = "red", linetype= "dashed") 

LatArid41to80

ggsave("LatArid41to80.pdf", plot = LatArid41to80, height = 6, width = 6, dpi = 300)
```
Load longitude data for arid species
```{r}
species_list <- unique(Arid_Species$Species) 

i = 1 

species_list[i] 

df_temp <- Arid_Species %>% filter(Species == species_list[i]) 
  lm_temp <- lm(decimalLongitude ~ year, data = df_temp) 
  summary_temp <- summary(lm_temp) 
  p_temp <- pf(summary_temp$fstatistic[1], 
               summary_temp$fstatistic[2],
               summary_temp$fstatistic[3],lower.tail=F)

  summary_temp

  stats_temp <- data.frame( 
    species = species_list[i], 
    formula = "lm(decimalLongitude ~ year)",
    n = nrow(df_temp),
    year_effect = lm_temp[["coefficients"]][["year"]],
      year_se = summary_temp[["coefficients"]][["year","Std. Error"]],
    r_sq = summary_temp[["r.squared"]],
    r_squ_adj = summary_temp[["adj.r.squared"]],
    p_val = p_temp,
    sig = p_temp < 0.05 
    )

   rm(i, df_temp, lm_temp, summary_temp, p_temp, stats_temp)
```
Creating graph for longitude for the Arid species 1-40
```{r}
summary_stats_3<-c()

for (i in 1:40) {

df_temp <- Arid_Species %>% filter(Species == species_list[i]) 
  lm_temp <- lm(decimalLongitude ~ year, data = df_temp) 
  summary_temp <- summary(lm_temp) 
    p_temp <- pf(summary_temp$fstatistic[1], 
               summary_temp$fstatistic[2],
               summary_temp$fstatistic[3],lower.tail=F)
    
  stats_temp <- data.frame( 
    species = species_list[i], 
    formula = "lm(decimalLongitude ~ year)", 
    n = nrow(df_temp), 
    year_effect = lm_temp[["coefficients"]][["year"]], 
    year_se = summary_temp[["coefficients"]][["year","Std. Error"]],
    r_sq = summary_temp[["r.squared"]], 
    r_squ_adj = summary_temp[["adj.r.squared"]],
    p_val = p_temp,
    sig = p_temp < 0.05 
    )

  summary_stats_3 <- bind_rows(summary_stats_3, stats_temp) 

   rm(df_temp, lm_temp, summary_temp, p_temp, stats_temp)
}

summary_stats_3 

cbPalette <- c("#999999", "#000000")

#Create plot of longitude shifts of arid species 1-40
LonSpecies1to40 <- ggplot(data = summary_stats_3, aes(year_effect, species,color=sig))+
  geom_point()+ scale_colour_manual(values = cbPalette) +
  xlab("Mean Rate of Longitude Shift (degrees/year)")+
  ylab("Arid Species") +
  geom_errorbar(aes(xmin=year_effect-year_se, xmax=year_effect+year_se))+
  theme_classic()+
  xlim(-0.13, 0.16)+
  theme(axis.text.x = element_text(angle = 45, hjust=1)) +
  theme(text = element_text(size = 13)) +
  geom_line() +
  geom_vline(xintercept = 0, colour = "red", linetype= "dashed")+
  scale_x_continuous(breaks = seq(-0.16,0.16, 0.08), limits = c(-0.16,0.16))+
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        axis.text.y = element_text(face="italic")) +
  theme(text = element_text(size = 13)) + 
  geom_line() +
  geom_vline(xintercept = 0, colour = "red", linetype= "dashed")

LonSpecies1to40

ggsave("LonArid1to40.pdf", plot = LonSpecies1to40, height = 6, width = 6, dpi = 300)
```

```{r}
summary_stats_4<-c()

for (i in 41:80) {

df_temp <- Arid_Species %>% filter(Species == species_list[i]) 
  lm_temp <- lm(decimalLongitude ~ year, data = df_temp) 
  summary_temp <- summary(lm_temp) 
    p_temp <- pf(summary_temp$fstatistic[1], 
               summary_temp$fstatistic[2],
               summary_temp$fstatistic[3],lower.tail=F)

 

  stats_temp <- data.frame( 
    species = species_list[i], 
    formula = "lm(decimalLongitude ~ year)", 
    n = nrow(df_temp), 
    year_effect = lm_temp[["coefficients"]][["year"]], 
    year_se = summary_temp[["coefficients"]][["year","Std. Error"]], 
    r_sq = summary_temp[["r.squared"]], 
    r_squ_adj = summary_temp[["adj.r.squared"]], 
    p_val = p_temp,
    sig = p_temp < 0.05 
    )

  summary_stats_4 <- bind_rows(summary_stats_4, stats_temp) 

   rm(df_temp, lm_temp, summary_temp, p_temp, stats_temp)
}

summary_stats_4 

#Create plot of longitude shifts of arid species 41-80
LonSpecies41to80 <- ggplot(data = summary_stats_4, aes(year_effect, species,color=sig))+
  geom_point()+ scale_colour_manual(values = cbPalette) +
  xlab("Mean Rate of Longitude Shift (degrees/year)")+
  ylab("Arid Species") +
  geom_errorbar(aes(xmin=year_effect-year_se, xmax=year_effect+year_se))+
  theme_classic()+
  scale_x_continuous(breaks = seq(-0.16,0.16, 0.08), limits = c(-0.16,0.16))+
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        axis.text.y = element_text(face="italic")) +
  theme(text = element_text(size = 13)) + 
  geom_line() +
  geom_vline(xintercept = 0, colour = "red", linetype= "dashed")

LonSpecies41to80

ggsave("LonArid41to80.pdf", plot = LonSpecies41to80, height = 6, width = 6, dpi = 300)
```
Running latitude linear regression for Acacia baeuerlenii (Mesic)
```{r}
species_list_mesic <- unique(Mesic_Species$Species) #make list of species

i_m = 1 

species_list_mesic[i_m] 

df_temp_m <- Mesic_Species %>% filter(Species == species_list_mesic[i_m]) 
  lm_temp_m <- lm(decimalLatitude ~ year, data = df_temp_m) 
  summary_temp_m <- summary(lm_temp_m) 
  p_temp_m <- pf(summary_temp_m$fstatistic[1],
               summary_temp_m$fstatistic[2],
               summary_temp_m$fstatistic[3],lower.tail=F)

  stats_temp_m <- data.frame(
    species = species_list_mesic[i_m],
    formula = "lm(decimalLatitude ~ year)",
    n = nrow(df_temp_m),
    year_effect = lm_temp_m[["coefficients"]][["year"]],
    year_se = summary_temp_m[["coefficients"]][["year","Std. Error"]],
    r_sq = summary_temp_m[["r.squared"]],
    r_squ_adj = summary_temp_m[["adj.r.squared"]],
    p_val = p_temp_m,
    sig = p_temp_m < 0.05 
    ) 
  
  summary_stats_mesic <- stats_temp_m
  
  rm(i_m, df_temp_m, lm_temp_m, summary_temp_m, p_temp_m, stats_temp_m)
```
Creating graphs for mesic latitude
```{r}
summary_stats_5<-c()

for (i_m in 1:38) { #loop for species 1 to 38 (Acacia baeuerlenii - Eucalyptus infera)

df_temp_m <- Mesic_Species %>% filter(Species == species_list_mesic[i_m]) #filter DataFrame by your study species
  lm_temp_m <- lm(decimalLatitude ~ year, data = df_temp_m) #run the linear model
  summary_temp_m <- summary(lm_temp_m) #save the summary stats as well
  p_temp_m <- pf(summary_temp_m$fstatistic[1],
               summary_temp_m$fstatistic[2],
               summary_temp_m$fstatistic[3],lower.tail=F)

  stats_temp_m <- data.frame( #make a table of summary statistics:
    species = species_list_mesic[i_m], #what species is this?
    formula = "lm(decimalLatitude ~ year)", #what formula did we use?
    n = nrow(df_temp_m), #number of records
    year_effect = lm_temp_m[["coefficients"]][["year"]], #effect of year
    year_se = summary_temp_m[["coefficients"]][["year","Std. Error"]], #standard error of the slope
    r_sq = summary_temp_m[["r.squared"]], #r squared
    r_squ_adj = summary_temp_m[["adj.r.squared"]], #adjusted r squared
    p_val = p_temp_m,
    sig = p_temp_m < 0.05 #is the p val significant
    ) 

  summary_stats_5 <- bind_rows(summary_stats_5, stats_temp_m) #attach the new data onto the summary table

   rm(df_temp, lm_temp_m, summary_temp_m, p_temp_m, stats_temp_m) #remove temporary data now that everything is on the big table

}

summary_stats_5 #have a look at summary table

LatMesic1to38 <- ggplot(data = summary_stats_5, aes(year_effect, species,color=sig))+
  geom_point()+ scale_colour_manual(values = cbPalette) +
  xlab("Mean Rate of Latitude Shift (degrees/year)")+
  ylab("Mesic Species") +
  geom_errorbar(aes(xmin=year_effect-year_se, xmax=year_effect+year_se))+
  theme_classic()+
  #scale_x_continuous(breaks = seq(-0.06,0.06, 0.03), limits = c(-0.06,0.06))+
  scale_x_continuous(breaks = seq(-0.08,0.12, 0.04), limits = c(-0.08,0.12))+
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        axis.text.y = element_text(face="italic")) +
  theme(text = element_text(size = 13)) + 
  geom_line() +
  geom_vline(xintercept = 0, colour = "red", linetype= "dashed")


LatMesic1to38

ggsave("LatMesic1to38.pdf", plot = LatMesic1to38, height = 6, width = 6, dpi = 300)
```
#Creating graphs for mesic latitude
```{r}
summary_stats_6<-c()

for (i_m in 39:76) { #loop for species 39 to 76 (Eucalyptus magnificata - Uromyrtus australis)

df_temp_m <- Mesic_Species %>% filter(Species == species_list_mesic[i_m]) #filter DataFrame by your study species
  lm_temp_m <- lm(decimalLatitude ~ year, data = df_temp_m) #run the linear model
  summary_temp_m <- summary(lm_temp_m) #save the summary stats as well
  p_temp_m <- pf(summary_temp_m$fstatistic[1],
               summary_temp_m$fstatistic[2],
               summary_temp_m$fstatistic[3],lower.tail=F)

  stats_temp_m <- data.frame( #make a table of summary statistics:
    species = species_list_mesic[i_m], #what species is this?
    formula = "lm(decimalLatitude ~ year)", #what formula did we use?
    n = nrow(df_temp_m), #number of records
    year_effect = lm_temp_m[["coefficients"]][["year"]], #effect of year
    year_se = summary_temp_m[["coefficients"]][["year","Std. Error"]], #standard error of the slope
    r_sq = summary_temp_m[["r.squared"]], #r squared
    r_squ_adj = summary_temp_m[["adj.r.squared"]], #adjusted r squared
    p_val = p_temp_m,
    sig = p_temp_m < 0.05 #is the p val significant
    ) 

  summary_stats_6 <- bind_rows(summary_stats_6, stats_temp_m) #attach the new data onto the summary table

   rm(df_temp, lm_temp_m, summary_temp_m, p_temp_m, stats_temp_m) #remove temporary data now that everything is on the big table

}

summary_stats_6 #have a look at summary table

cbPalette <- c("#999999", "#000000")

LatMesic39to76 <- ggplot(data = summary_stats_6, aes(year_effect, species, color=sig))+
  geom_point()+ scale_colour_manual(values = cbPalette) +
  xlab("Mean Rate of Latitude Shift (degrees/year)")+
  ylab("Mesic Species") +
  geom_errorbar(aes(xmin=year_effect-year_se, xmax=year_effect+year_se))+
  theme_classic()+
  #scale_x_continuous(breaks = seq(-0.06,0.06, 0.03), limits = c(-0.06,0.06))+
  scale_x_continuous(breaks = seq(-0.08,0.12, 0.04), limits = c(-0.08,0.12))+
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        axis.text.y = element_text(face="italic")) +
  theme(text = element_text(size = 13)) + 
  geom_line() +
  geom_vline(xintercept = 0, colour = "red", linetype= "dashed")

LatMesic39to76

ggsave("LatMesic39to76.pdf", plot = LatMesic39to76, height = 6, width = 6, dpi = 300)

```
#Running longitude linear regression for Acacia baeuerlenii (Mesic)
```{r}
species_list_mesic <- unique(Mesic_Species$Species) #make list of species

i_m = 1 #do the first species manually to troubleshoot

species_list_mesic[i_m] # check what this species is for funsies

df_temp_m <- Mesic_Species %>% filter(Species == species_list_mesic[i_m]) #filter DataFrame by your study species
  lm_temp_m <- lm(decimalLongitude ~ year, data = df_temp_m) #run the linear model
  summary_temp_m <- summary(lm_temp_m) #save the summary stats as well
  p_temp_m <- pf(summary_temp_m$fstatistic[1],
               summary_temp_m$fstatistic[2],
               summary_temp_m$fstatistic[3],lower.tail=F)

  stats_temp_m <- data.frame( #make a table of summary statistics:
    species = species_list_mesic[i_m], #what species is this?
    formula = "lm(decimalLongitude ~ year)", #what formula did we use?
    n = nrow(df_temp_m), #number of records
    year_effect = lm_temp_m[["coefficients"]][["year"]], #effect of year
    year_se = summary_temp_m[["coefficients"]][["year","Std. Error"]], #standard error of the slope
    r_sq = summary_temp_m[["r.squared"]], #r squared
    r_squ_adj = summary_temp_m[["adj.r.squared"]], #adjusted r squared
    p_val = p_temp_m,
    sig = p_temp_m < 0.05 #is the p val significant
    ) 
  
  summary_stats_mesic <- stats_temp_m #save this as the first row of your list of summary statistics
  
   rm(i_m, df_temp_m, lm_temp_m, summary_temp_m, p_temp_m, stats_temp_m) #remove temporary data now that everything is on the big table
```
#Creating graphs for mesic longitude
```{r}
summary_stats_7<-c()

for (i_m in 1:38) { #loop for species 1 to 38 (Acacia baeuerlenii - Eucalyptus infera)

df_temp_m <- Mesic_Species %>% filter(Species == species_list_mesic[i_m]) #filter DataFrame by your study species
  lm_temp_m <- lm(decimalLongitude ~ year, data = df_temp_m) #run the linear model
  summary_temp_m <- summary(lm_temp_m) #save the summary stats as well
  p_temp_m <- pf(summary_temp_m$fstatistic[1],
               summary_temp_m$fstatistic[2],
               summary_temp_m$fstatistic[3],lower.tail=F)

  stats_temp_m <- data.frame( #make a table of summary statistics:
    species = species_list_mesic[i_m], #what species is this?
    formula = "lm(decimalLongitude ~ year)", #what formula did we use?
    n = nrow(df_temp_m), #number of records
    year_effect = lm_temp_m[["coefficients"]][["year"]], #effect of year
    year_se = summary_temp_m[["coefficients"]][["year","Std. Error"]], #standard error of the slope
    r_sq = summary_temp_m[["r.squared"]], #r squared
    r_squ_adj = summary_temp_m[["adj.r.squared"]], #adjusted r squared
    p_val = p_temp_m,
    sig = p_temp_m < 0.05 #is the p val significant
    ) 

  summary_stats_7 <- bind_rows(summary_stats_7, stats_temp_m) #attach the new data onto the summary table

   rm(df_temp, lm_temp_m, summary_temp_m, p_temp_m, stats_temp_m) #remove temporary data now that everything is on the big table

}

summary_stats_7 #have a look at summary table

LonMesic1to38 <- ggplot(data = summary_stats_7, aes(year_effect, species,color=sig))+
  geom_point()+ scale_colour_manual(values = cbPalette) +
  xlab("Mean Rate of Longitude Shift (degrees/year)")+
  ylab("Mesic Species") +
  geom_errorbar(aes(xmin=year_effect-year_se, xmax=year_effect+year_se))+
  theme_classic()+
  scale_x_continuous(breaks = seq(-0.03,0.03, 0.01), limits = c(-0.03,0.03))+
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        axis.text.y = element_text(face="italic")) +
  theme(text = element_text(size = 13)) + 
  geom_line() +
  geom_vline(xintercept = 0, colour = "red", linetype= "dashed")

LonMesic1to38

ggsave("LonMesic1to38.pdf", plot = LonMesic1to38, height = 6, width = 6, dpi = 300)

LonMesic1to38
```
#Creating graphs for mesic longitude
```{r}
summary_stats_8<-c()

for (i_m in 39:76) { #loop for species 39 to 76 (Eucalyptus magnificata - Uromyrtus australis)

df_temp_m <- Mesic_Species %>% filter(Species == species_list_mesic[i_m]) #filter DataFrame by your study species
  lm_temp_m <- lm(decimalLongitude ~ year, data = df_temp_m) #run the linear model
  summary_temp_m <- summary(lm_temp_m) #save the summary stats as well
  p_temp_m <- pf(summary_temp_m$fstatistic[1],
               summary_temp_m$fstatistic[2],
               summary_temp_m$fstatistic[3],lower.tail=F)

  stats_temp_m <- data.frame( #make a table of summary statistics:
    species = species_list_mesic[i_m], #what species is this?
    formula = "lm(decimalLongitude ~ year)", #what formula did we use?
    n = nrow(df_temp_m), #number of records
    year_effect = lm_temp_m[["coefficients"]][["year"]], #effect of year
    year_se = summary_temp_m[["coefficients"]][["year","Std. Error"]], #standard error of the slope
    r_sq = summary_temp_m[["r.squared"]], #r squared
    r_squ_adj = summary_temp_m[["adj.r.squared"]], #adjusted r squared
    p_val = p_temp_m,
    sig = p_temp_m < 0.05 #is the p val significant
    ) 

  summary_stats_8 <- bind_rows(summary_stats_8, stats_temp_m) #attach the new data onto the summary table

   rm(df_temp, lm_temp_m, summary_temp_m, p_temp_m, stats_temp_m) #remove temporary data now that everything is on the big table

}

summary_stats_8 #have a look at summary table

cbPalette <- c("#999999", "#000000")

LonMesic39to76 <- ggplot(data = summary_stats_8, aes(year_effect, species,color=sig))+
  geom_point()+ scale_colour_manual(values = cbPalette) +
  xlab("Mean Rate of Longitude Shift (degrees/year)")+
  ylab("Mesic Species") +
  geom_errorbar(aes(xmin=year_effect-year_se, xmax=year_effect+year_se))+
  theme_classic()+
  scale_x_continuous(breaks = seq(-0.03,0.03, 0.01), limits = c(-0.03,0.03))+
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        axis.text.y = element_text(face="italic")) +
  theme(text = element_text(size = 13)) + 
  geom_line() +
  geom_vline(xintercept = 0, colour = "red", linetype= "dashed")

LonMesic39to76

ggsave("LonMesic39to76.pdf", plot = LonMesic39to76, height = 6, width = 6, dpi = 300)
```
Combine Lat Plots
```{r}
LatPlots <- grid.arrange(grobs = (LatArid1to40, LatArid41to80, LatMesic1to38, LatMesic39to76, ncol = 2) 
                         
LonPlots <- grid.arrange(grobs = (LonArid1to40, LonArid41to80, LonMesic1to38, LonMesic39to76, ncol = 2) 
```

