Install Packages
```{r}
#install.packages("dplyr", dependencies = TRUE)
library(dplyr)
remove.packages("rlang")
#install_version("quantreg", "5.94")
library(quantreg)
#install.packages("tidyverse")
library(utils)
#install.packages("broom")
library(broom)
remove.packages("broom")
#install.packages("writexl")
library(writexl)
```
Loading arid and mesic data
```{r}
Final_Arid <- read.csv("Final_Arid.csv")
Final_Mesic <-read.csv("Final_Mesic.csv")
```
Running latitude quantile regression for Acacia Abrupta to find its p-value to determine sig contraction and expansion responses.
```{r}
species_list_arid <- unique(Final_Arid$Species) #Produces a list of species

i_a = 1 #Run for first species to troubleshoot

species_list_arid[i_a] # Check the species name is correct

df_temp_a <- Final_Arid %>% filter(Species == species_list_arid[i_a]) #filter DataFrame by the study species

fit_a <- lm(decimalLatitude ~year, data= df_temp_a)

quantiles_05 <- rq(fit_a, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_a, tau = c(0.95)) %>% summary(se="boot")


 q0.5 <-  data.frame(species=species_list_arid[i_a], tau=  quantiles_05[["tau"]],
                     y0= quantiles_05[["coefficients"]]["(Intercept)", "Value"],
year_effect=  quantiles_05[["coefficients"]]["year", "Value"],
year_SE=quantiles_05[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_05[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_05[["coefficients"]]["year", "Pr(>|t|)"] < 0.05) #check if the p val significant


 q.95 <- data.frame(species=species_list_arid[i_a], tau=  quantiles_95[["tau"]],
                                         y0= quantiles_95[["coefficients"]]["(Intercept)", "Value"],
year_effect=  quantiles_95[["coefficients"]]["year", "Value"],
year_SE=quantiles_95[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_95[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_95[["coefficients"]]["year", "Pr(>|t|)"] < 0.05) #check if the p val significant

  quant_lat <- rbind(q0.5, q.95) %>% mutate(pv= if_else(year_pvalue>0.05, "dashed", "solid"))
```
Running latitude quantile regression for ALL arid species to find their respective p-values to determine sig contraction and expansion responses.
```{r}
quant_lat = c()

for (i_a in 1:80) { #loop for species 1 to 80

species_list_arid[i_a] 
  
df_temp_a <- Final_Arid %>% filter(Species == species_list_arid[i_a])

fit_a <- lm(decimalLatitude ~year, data= df_temp_a)

quantiles_05 <- rq(fit_a, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_a, tau = c(0.95)) %>% summary(se="boot")

 q0.5 <-  data.frame(species=species_list_arid[i_a],tau=  quantiles_05[["tau"]],
year_effect=  quantiles_05[["coefficients"]]["year", "Value"],
year_SE=quantiles_05[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_05[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_05[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)

 q.95 <- data.frame(species=species_list_arid[i_a],tau=  quantiles_95[["tau"]],
year_effect=  quantiles_95[["coefficients"]]["year", "Value"],
year_SE=quantiles_95[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_95[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_95[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)

quant_prel <- bind_rows(q0.5, q.95)
quant_lat <- bind_rows(quant_lat, quant_prel)
}

quant_lat #have a look at summary table

print(quant_lat)

write.csv(quant_lat, "/Users/Euan/Desktop/Honours/Historic data/quantiles_lat_arid.csv")
```
Longitude quantile regression for Acacia abrupta
```{r}
species_list_arid <- unique(Final_Arid$Species)

i_a = 1 

species_list_arid[i_a]

df_temp_a <- Final_Arid %>% filter(Species == species_list_arid[i_a])

fit_a_l <- lm(decimalLongitude ~year, data= df_temp_a)

quantiles_05 <- rq(fit_a_l, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_a_l, tau = c(0.95)) %>% summary(se="boot")


 q0.5 <-  data.frame(species=species_list_arid[i_a], tau=  quantiles_05[["tau"]],
year_effect=  quantiles_05[["coefficients"]]["year", "Value"],
year_SE=quantiles_05[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_05[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_05[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)


 q.95 <- data.frame(species=species_list_arid[i_a], tau=  quantiles_95[["tau"]],
year_effect=  quantiles_95[["coefficients"]]["year", "Value"],
year_SE=quantiles_95[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_95[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_95[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)

  quant_lon <- rbind(q0.5, q.95)
```
Longitude quantile regression for ALL arid species
```{r}
quant_lon = c()

for (i_a in 1:80) {

species_list_arid[i_a]
  
df_temp_a <- Final_Arid %>% filter(Species == species_list_arid[i_a])

fit_a_l <- lm(decimalLongitude ~year, data= df_temp_a)

quantiles_05 <- rq(fit_a_l, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_a_l, tau = c(0.95)) %>% summary(se="boot")

 q0.5 <-  data.frame(species=species_list_arid[i_a],tau=  quantiles_05[["tau"]],
year_effect=  quantiles_05[["coefficients"]]["year", "Value"],
year_SE=quantiles_05[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_05[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_05[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)

 q.95 <- data.frame(species=species_list_arid[i_a],tau=  quantiles_95[["tau"]],
year_effect=  quantiles_95[["coefficients"]]["year", "Value"],
year_SE=quantiles_95[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_95[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_95[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)

quant_prel <- bind_rows(q0.5, q.95)
quant_lon <- bind_rows(quant_lon, quant_prel)
}

quant_lon 

print(quant_lon)

write_xlsx(quant_lon, "/Users/Euan/Desktop/Honours/Historic data/quantiles_lon_arid.csv")
```

Running latitude quantile regression for Acacia baeu to find its p-value to determine sig contraction and expansion responses.
```{r}
species_list_mesic <- unique(Final_Mesic$Species) 

i_m = 1 

species_list_mesic[i_m] 

df_temp_m <- Final_Mesic %>% filter(Species == species_list_mesic[i_m])

fit_m <- lm(decimalLatitude ~year, data= df_temp_m)

quantiles_05 <- rq(fit_m, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_m, tau = c(0.95)) %>% summary(se="boot")


 q0.5_m <-  data.frame(species=species_list_mesic[i_m], tau=  quantiles_05[["tau"]],
year_effect=  quantiles_05[["coefficients"]]["year", "Value"],
year_SE=quantiles_05[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_05[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_05[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)


 q.95_m <- data.frame(species=species_list_mesic[i_m], tau=  quantiles_95[["tau"]],
year_effect=  quantiles_95[["coefficients"]]["year", "Value"],
year_SE=quantiles_95[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_95[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_95[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)

  quant_lat_m <- rbind(q0.5_m, q.95_m)
```

Running latitude quantile regression for ALL mesic species to find their respective p-values to determine sig contraction and expansion responses.
```{r}
quant_lat_m = c()

for (i_m in 1:76) { #loop for species 1 to 76

species_list_mesic[i_m] 
  
df_temp_m <- Final_Mesic %>% filter(Species == species_list_mesic[i_m]) 
fit_m <- lm(decimalLatitude ~year, data= df_temp_m)

quantiles_05 <- rq(fit_m, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_m, tau = c(0.95)) %>% summary(se="boot")

 q0.5_m <-  data.frame(species=species_list_mesic[i_m],tau=  quantiles_05[["tau"]],
year_effect=  quantiles_05[["coefficients"]]["year", "Value"],
year_SE=quantiles_05[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_05[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_05[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)

 q.95_m <- data.frame(species=species_list_mesic[i_m],tau=  quantiles_95[["tau"]],
year_effect=  quantiles_95[["coefficients"]]["year", "Value"],
year_SE=quantiles_95[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_95[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_95[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)

quant_prel_m <- bind_rows(q0.5_m, q.95_m)
quant_lat_m <- bind_rows(quant_lat_m, quant_prel_m)
}

quant_lat_m

print(quant_lat_m)

write_xlsx(quant_lat_m, "/Users/Euan/Desktop/Honours/Historic data/quantiles_lat_mesic.csv")
```
Longitude quantile regression for Acacia baeuerlenii
```{r}
species_list_mesic <- unique(Final_Mesic$Species)

i_m = 1 

species_list_arid[i_a] 

df_temp_m <- Final_Mesic %>% filter(Species == species_list_mesic[i_m])

fit_m_l <- lm(decimalLongitude ~year, data= df_temp_m)

quantiles_05 <- rq(fit_m_l, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_m_l, tau = c(0.95)) %>% summary(se="boot")


 q0.5_m <-  data.frame(species=species_list_mesic[i_m], tau=  quantiles_05[["tau"]],
year_effect=  quantiles_05[["coefficients"]]["year", "Value"],
year_SE=quantiles_05[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_05[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_05[["coefficients"]]["year", "Pr(>|t|)"] < 0.05) 


 q.95_m <- data.frame(species=species_list_mesic[i_m], tau=  quantiles_95[["tau"]],
year_effect=  quantiles_95[["coefficients"]]["year", "Value"],
year_SE=quantiles_95[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_95[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_95[["coefficients"]]["year", "Pr(>|t|)"] < 0.05) 

  quant_lon_m <- rbind(q0.5, q.95)
```

Longitude quantile regression for ALL mesic species
```{r}
quant_lon_m = c()

for (i_m in 1:76) { 

species_list_mesic[i_m]
  
df_temp_m <- Final_Mesic %>% filter(Species == species_list_mesic[i_m])

fit_m_l <- lm(decimalLongitude ~year, data= df_temp_m)

quantiles_05 <- rq(fit_m_l, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_m_l, tau = c(0.95)) %>% summary(se="boot")

 q0.5_m <-  data.frame(species=species_list_mesic[i_m],tau=  quantiles_05[["tau"]],
year_effect=  quantiles_05[["coefficients"]]["year", "Value"],
year_SE=quantiles_05[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_05[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_05[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)

 q.95_m <- data.frame(species=species_list_mesic[i_m],tau=  quantiles_95[["tau"]],
year_effect=  quantiles_95[["coefficients"]]["year", "Value"],
year_SE=quantiles_95[["coefficients"]]["year", "Std. Error"],
year_pvalue= quantiles_95[["coefficients"]]["year", "Pr(>|t|)"],
sig =  quantiles_95[["coefficients"]]["year", "Pr(>|t|)"] < 0.05)

quant_prel_m <- bind_rows(q0.5_m, q.95_m)
quant_lon_m <- bind_rows(quant_lon_m, quant_prel_m)
}

quant_lon_m

print(quant_lon_m)

write.csv(quant_lon_m, "/Users/Euan/Desktop/Honours/Historic data/quantiles_lon_mesic.csv")
```

P-value adjustments for the study species
```{r}
#Arid
LatQuantArid <-read.csv("quantiles_lat_arid.csv")
LatQuantArid$adjust_pvalue <- p.adjust(LatQuantArid$year_pvalue, method = "holm")
write.csv(LatQuantArid, "/Users/Euan/Desktop/Honours/Historic data/quantiles_lat_arid_pcorrected.csv")

LonQuantArid <-read.csv("quantiles_lon_arid.csv")
LonQuantArid$adjust_pvalue <- p.adjust(LonQuantArid$year_pvalue, method = "holm")
write.csv(LonQuantArid, "/Users/Euan/Desktop/Honours/Historic data/quantiles_lon_arid_pcorrected.csv")

#Mesic
LatQuantMesic <-read.csv("quantiles_lat_mesic.csv")
LatQuantMesic$adjust_pvalue <- p.adjust(LatQuantMesic$year_pvalue, method = "holm")
write.csv(LatQuantMesic, "/Users/Euan/Desktop/Honours/Historic data/quantiles_lat_mesic_pcorrected.csv")

LonQuantMesic <-read.csv("quantiles_lon_mesic.csv")
LonQuantMesic$adjust_pvalue <- p.adjust(LonQuantMesic$year_pvalue, method = "holm")
write.csv(LonQuantMesic, "/Users/Euan/Desktop/Honours/Historic data/quantiles_lon_mesic_pcorrected.csv")
```
Analysis of variance - significant differences between range edges for study species
```{r}
#Arid
Lat_edge_sig_m <- lm(tau ~ year_effect, data = quant_lat_m)
mesic_lat_ANOVA <- anova(Lat_edge_sig_m)

Lon_edge_sig_m <- lm(tau ~ year_effect, data = quant_lon_m)
mesic_lon_ANOVA <- anova(Lon_edge_sig_m)
mesic_lon_ANOVA

#Mesic
Lat_edge_sig_a <- lm(tau ~ year_effect, data = quant_lat)
arid_lat_ANOVA <- anova(Lat_edge_sig_a)

Lon_edge_sig_a <- lm(tau ~ year_effect, data = quant_lon)
arid_lon_ANOVA <- anova(Lon_edge_sig_a)
arid_lon_ANOVA
```