Install Packages
```{r}
library(dplyr)
library(quantreg)
library(utils)
library(writexl)
library(ggplot2)
library(gridExtra)
library(grid)
```
Loading arid and mesic data
```{r}
Final_Arid <- read.csv("Final_Arid.csv")
Final_Mesic <-read.csv("Final_Mesic.csv")
```

Running latitude quantile regression for Acacia Abrupta to find its p-value to determine sig contraction and expansion responses.
```{r}
species_list_arid <- unique(Final_Arid$Species)

i_a = 1

species_list_arid[i_a]

df_temp_a <- Final_Arid %>% filter(Species == species_list_arid[i_a])

fit_a <- lm(decimalLatitude ~year, data= df_temp_a)

quantiles_05 <- rq(fit_a, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_a, tau = c(0.95)) %>% summary(se="boot")

#Create statistics for lower quantile (5th) to plot

qrpv05<-  data.frame(species=species_list_arid[i_a], tau=  quantiles_05[["tau"]],
                    y0= coef(quantiles_05)[1],
                    slope=coef(quantiles_05)[2],
                    slope_pv= coef(quantiles_05)[8],
                    slope_sig = coef(quantiles_05)[8]<0.05)

#Create statistics for upper quantile (95th) to plot

qrpv95<-  data.frame(species=species_list_arid[i_a], tau=  quantiles_05[["tau"]],
                     y0= coef(quantiles_95)[1],
                     slope=coef(quantiles_95)[2],
                     slope_pv= coef(quantiles_95)[8],
                     slope_sig = coef(quantiles_95)[8]<0.05)

 quant_lat <- rbind(qrpv05, qrpv95)
```
Running latitude quantile regression for ALL arid species to find their respective p-values to determine sig contraction and expansion responses.
```{r}
quant_lat = c()

for (i_a in 1:80) { #loop for species 1 to 80

species_list_arid <- unique(Final_Arid$Species)

i_a = 1

species_list_arid[i_a]

df_temp_a <- Final_Arid %>% filter(Species == species_list_arid[i_a])

fit_a <- lm(decimalLatitude ~year, data= df_temp_a)

quantiles_05 <- rq(fit_a, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_a, tau = c(0.95)) %>% summary(se="boot")

#Create statistics for lower quantile (5th) to plot

qrpv05<-  data.frame(species=species_list_arid[i_a], tau=  quantiles_05[["tau"]],
                    y0= coef(quantiles_05)[1],
                    slope=coef(quantiles_05)[2],
                    slope_pv= coef(quantiles_05)[8],
                    slope_sig = coef(quantiles_05)[8]<0.05)

#Create statistics for upper quantile (95th) to plot

qrpv95<-  data.frame(species=species_list_arid[i_a], tau=  quantiles_05[["tau"]],
                     y0= coef(quantiles_95)[1],
                     slope=coef(quantiles_95)[2],
                     slope_pv= coef(quantiles_95)[8],
                     slope_sig = coef(quantiles_95)[8]<0.05)

  quant_prel <- bind_rows(qrpv05, qrpv95)
  quant_lat <- bind_rows(quant_lat, quant_prel)
}
```
Latitude quantile regression for individual arid species
```{r}
Lat1 <- filter(Final_Arid, Species =="Acacia abrupta") %>%
  rq(decimalLatitude ~ year, tau=c(.05,0.95),.)

Lat1df<- data.frame(cbind(y=Lat1[["y"]],
                      x=Lat1[["x"]][,2],
                        n.05=Lat1[["fitted.values"]][,1], 
                      n95=Lat1[["fitted.values"]][,2]))

ggplot(data=df_temp_a, aes(x=year, y=decimalLatitude))+
    geom_point(size = 3.5)+
     coord_cartesian(xlim = c(1915, 2022), ylim = c(-35, -20)) + 
    geom_abline(aes(intercept=coef(quantiles_95)[1], slope=coef(quantiles_95)[2], 
                    linetype=qrpv95$slope_sig), col = "dark orange", size = 1)+
    geom_abline(aes(intercept=coef(quantiles_05)[1], slope=coef(quantiles_05)[2], 
                    linetype=qrpv05$slope_sig), col = "dark orange", size = 1)+
    scale_linetype_manual(values = c("FALSE" = "dashed", "TRUE" = "solid"))+
    labs(x="", y="")+
    theme_classic()+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())+
    theme(legend.position = "none",
          axis.text.x = element_text(size =22),
          axis.text.y = element_text(size =22),
          plot.title = element_text(size=25))
  
  summary(Lat1, se = "boot")
```
Running latitude quantile regression for Acacia Abrupta (Arid - Euan) to find its p-value to determine sig contraction and expansion responses.
```{r}
spp = unique(Final_Arid$Species)

spp_species_plots = list()

for(species in spp) {

  df_temp_a <- Final_Arid %>% filter(Species == species) #filter DataFrame by your study species

  fit_a <- lm(decimalLatitude ~year, data= df_temp_a)

  quantiles_05 <- rq(fit_a, tau = c(0.05)) %>% summary(se="boot")  #we need to bootstrap for a p-value
  quantiles_95 <- rq(fit_a, tau = c(0.95)) %>% summary(se="boot")

  qrpv05<-  data.frame(species=species,
                       tau=  quantiles_05[["tau"]],
                       y0= coef(quantiles_05)[1],
                       slope=coef(quantiles_05)[2],
                       slope_pv= coef(quantiles_05)[8],
                       slope_sig = coef(quantiles_05)[8]<0.05)

  qrpv95<-  data.frame(species=species,
                       tau=  quantiles_95[["tau"]],
                       y0= coef(quantiles_95)[1],
                       slope=coef(quantiles_95)[2],
                       slope_pv= coef(quantiles_95)[8],
                       slope_sig = coef(quantiles_95)[8]<0.05)

  spp_species_plots[[species]] = ggplot(data=df_temp_a,
                                        aes(year, decimalLatitude)) +
    geom_point(size = 3.5)+
    coord_cartesian(xlim = c(1915, 2022), ylim = c(-35, -20)) +
    geom_abline(aes(intercept=coef(quantiles_95)[1], slope=coef(quantiles_95)[2],
                    linetype=qrpv95$slope_sig), col = "dark orange", size = 1)+
    geom_abline(aes(intercept=coef(quantiles_05)[1], slope=coef(quantiles_05)[2],
                    linetype=qrpv05$slope_sig), col = "dark orange", size = 1)+
    scale_linetype_manual(values = c("FALSE" = "dashed", "TRUE" = "solid"))+
    labs(x="", y="")+
    theme_classic()+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())+
    theme(legend.position = "none",
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          plot.title = element_text(size=25))+
    ggtitle(species)

  print(spp_species_plots[[species]])

ggsave(spp_species_plots[[species]],
      file=paste0("Lat_Arid_quantreg", species,".pdf"),
      width = 15, height = 10, units = "cm", dpi=300)
}
```
Running longitude quantile regression for ALL arid species to find their respective p-values to determine sig contraction and expansion responses.
```{r}
species_list_arid <- unique(Final_Arid$Species)

i_a = 1

species_list_arid[i_a]

df_temp_a <- Final_Arid %>% filter(Species == species_list_arid[i_a])

fit_a <- lm(decimalLongitude ~year, data= df_temp_a)

quantiles_05 <- rq(fit_a, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_a, tau = c(0.95)) %>% summary(se="boot")

#Create statistics for lower quantile (5th) to plot

qrpv05<-  data.frame(species=species_list_arid[i_a], tau=  quantiles_05[["tau"]],
                    y0= coef(quantiles_05)[1],
                    slope=coef(quantiles_05)[2],
                    slope_pv= coef(quantiles_05)[8],
                    slope_sig = coef(quantiles_05)[8]<0.05)

#Create statistics for upper quantile (95th) to plot

qrpv95<-  data.frame(species=species_list_arid[i_a], tau=  quantiles_05[["tau"]],
                     y0= coef(quantiles_95)[1],
                     slope=coef(quantiles_95)[2],
                     slope_pv= coef(quantiles_95)[8],
                     slope_sig = coef(quantiles_95)[8]<0.05)

 quant_lon <- rbind(qrpv05, qrpv95)
```
Create quantile longitude regression graph for all arid plants
```{r}
quant_lon = c()

for (i_a in 1:80) { #loop for species 1 to 80
  
  species_list_arid[i_a] # check what this species is for funsies
  
  df_temp_a <- Final_Arid %>% filter(Species == species_list_arid[i_a]) #filter DataFrame by your study species
  
  fit_a <- lm(decimalLongitude ~year, data= df_temp_a)
  
  quantiles_05 <- rq(fit_a, tau = c(0.05)) %>% summary(se="boot")
  quantiles_95 <- rq(fit_a, tau = c(0.95)) %>% summary(se="boot")
  
  qrpv05<-  data.frame(species=species_list_arid[i_a], 
                       tau=  quantiles_05[["tau"]],
                       y0= coef(quantiles_05)[1],
                       slope=coef(quantiles_05)[2],
                       slope_pv= coef(quantiles_05)[8],
                       slope_sig = coef(quantiles_05)[8]<0.05)
  
  qrpv95<-  data.frame(species=species_list_arid[i_a], 
                       tau=  quantiles_95[["tau"]],
                       y0= coef(quantiles_95)[1],
                       slope=coef(quantiles_95)[2],
                       slope_pv= coef(quantiles_95)[8],
                       slope_sig = coef(quantiles_95)[8]<0.05)

  quant_prel <- bind_rows(qrpv05, qrpv95)
  quant_lon <- bind_rows(quant_lon, quant_prel)
}
```
Longitude quantile regression for arid individual species
```{r}
Lon1 <- filter(Final_Arid, Species =="Acacia abrupta") %>%
  rq(decimalLongitude ~ year, tau=c(.05,0.95),.)

Lon1df<- data.frame(cbind(y=Lon1[["y"]],
                      x=Lon1[["x"]][,2],
                        n.05=Lon1[["fitted.values"]][,1], 
                      n95=Lon1[["fitted.values"]][,2]))

 ggplot(data=df_temp_a, aes(x=year, y=decimalLongitude))+
    geom_point(size = 3.5)+
   geom_smooth(method = "lm", se = FALSE)+
     coord_cartesian(xlim = c(1915, 2022), ylim = c(110, 150)) + 
    geom_abline(aes(intercept=coef(quantiles_95)[1], slope=coef(quantiles_95)[2], 
                    linetype=qrpv95$slope_sig), col = "dark orange", size = 1)+
    geom_abline(aes(intercept=coef(quantiles_05)[1], slope=coef(quantiles_05)[2], 
                    linetype=qrpv05$slope_sig), col = "dark orange", size = 1)+
    scale_linetype_manual(values = c("FALSE" = "dashed", "TRUE" = "solid"))+
    labs(x="", y="")+
    theme_classic()+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())+
    theme(legend.position = "none",
          axis.text.x = element_text(size =22),
          axis.text.y = element_text(size =22),
          plot.title = element_text(size=25))+
   ggtitle(species)
 
  summary(Lon1, se = "boot")
```
Longitude quantile regression for ALL arid species
```{r}
spp = unique(Final_Arid$Species)

spp_species_plots = list()

for(species in spp) {

  df_temp_a <- Final_Arid %>% filter(Species == species) #filter DataFrame by your study species

  fit_a <- lm(decimalLongitude ~year, data= df_temp_a)

  quantiles_05 <- rq(fit_a, tau = c(0.05)) %>% summary(se="boot")  #we need to bootstrap for a p-value
  quantiles_95 <- rq(fit_a, tau = c(0.95)) %>% summary(se="boot")

  qrpv05<-  data.frame(species=species,
                       tau=  quantiles_05[["tau"]],
                       y0= coef(quantiles_05)[1],
                       slope=coef(quantiles_05)[2],
                       slope_pv= coef(quantiles_05)[8],
                       slope_sig = coef(quantiles_05)[8]<0.05)

  qrpv95<-  data.frame(species=species,
                       tau=  quantiles_95[["tau"]],
                       y0= coef(quantiles_95)[1],
                       slope=coef(quantiles_95)[2],
                       slope_pv= coef(quantiles_95)[8],
                       slope_sig = coef(quantiles_95)[8]<0.05)

  spp_species_plots[[species]] = ggplot(data=df_temp_a,
                                        aes(year, decimalLongitude)) +
    geom_point(size = 3.5)+
    coord_cartesian(xlim = c(1915, 2022), ylim = c(110, 150)) +
    geom_abline(aes(intercept=coef(quantiles_95)[1], slope=coef(quantiles_95)[2],
                    linetype=qrpv95$slope_sig), col = "dark orange", size = 1)+
    geom_abline(aes(intercept=coef(quantiles_05)[1], slope=coef(quantiles_05)[2],
                    linetype=qrpv05$slope_sig), col = "dark orange", size = 1)+
    scale_linetype_manual(values = c("FALSE" = "dashed", "TRUE" = "solid"))+
    labs(x="", y="")+
    theme_classic()+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())+
    theme(legend.position = "none",
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          plot.title = element_text(size=25))+
    ggtitle(species)

  print(spp_species_plots[[species]])
  
  ggsave(spp_species_plots[[species]],
         file=paste0("Lon_Arid_quantreg", species,".png"),
         width = 20, height = 15, units = "cm", dpi=300)
}
```
Create quantile latitude regression graph for first mesic plant
```{r}
species_list_mesic <- unique(Final_Mesic$Species)

i_m = 1

species_list_mesic[i_m]

df_temp_m <- Final_Mesic %>% filter(Species == species_list_mesic[i_m])

fit_m <- lm(decimalLatitude ~year, data= df_temp_m)

quantiles_05 <- rq(fit_m, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_m, tau = c(0.95)) %>% summary(se="boot")

#Create statistics for lower quantile (5th) to plot

qrpv05m<-  data.frame(species=species_list_mesic[i_m], tau=  quantiles_05[["tau"]],
                    y0= coef(quantiles_05)[1],
                    slope=coef(quantiles_05)[2],
                    slope_pv= coef(quantiles_05)[8],
                    slope_sig = coef(quantiles_05)[8]<0.05)

#Create statistics for upper quantile (95th) to plot

qrpv95m<-  data.frame(species=species_list_mesic[i_m], tau=  quantiles_05[["tau"]],
                     y0= coef(quantiles_95)[1],
                     slope=coef(quantiles_95)[2],
                     slope_pv= coef(quantiles_95)[8],
                     slope_sig = coef(quantiles_95)[8]<0.05)

 quant_lat_m <- rbind(qrpv05m, qrpv95m)
```
Create quantile latitude regression graph for all mesic plants
```{r}
quant_lat_m = c()

for (i_m in 1:76) { #loop for species 1 to 76
  
  species_list_mesic[i_m] # check what this species is for funsies
  
  df_temp_m <- Final_Mesic %>% filter(Species == species_list_mesic[i_m]) #filter DataFrame by your study species
  
  fit_m <- lm(decimalLatitude ~year, data= df_temp_m)
  
  quantiles_05 <- rq(fit_m, tau = c(0.05)) %>% summary(se="boot")
  quantiles_95 <- rq(fit_m, tau = c(0.95)) %>% summary(se="boot")
  
  qrpv05m<-  data.frame(species=species_list_mesic[i_m], 
                       tau=  quantiles_05[["tau"]],
                       y0= coef(quantiles_05)[1],
                       slope=coef(quantiles_05)[2],
                       slope_pv= coef(quantiles_05)[8],
                       slope_sig = coef(quantiles_05)[8]<0.05)
  
  qrpv95m<-  data.frame(species=species_list_mesic[i_m], 
                       tau=  quantiles_95[["tau"]],
                       y0= coef(quantiles_95)[1],
                       slope=coef(quantiles_95)[2],
                       slope_pv= coef(quantiles_95)[8],
                       slope_sig = coef(quantiles_95)[8]<0.05)

  quant_prel_m <- bind_rows(qrpv05m, qrpv95m)
  quant_lat_m <- bind_rows(quant_lat_m, quant_prel_m)
}
```
Create quantile latitude regression graph for individual mesic species
```{r}
Lat1m <- filter(Final_Mesic, Species =="Acacia baeuerlenii") %>%
  rq(decimalLatitude ~ year, tau=c(.05,0.95),.)

Lat1dfm<- data.frame(cbind(y=Lat1m[["y"]],
                      x=Lat1m[["x"]][,2],
                        n.05=Lat1m[["fitted.values"]][,1], 
                      n95=Lat1m[["fitted.values"]][,2]))

  ggplot(data=df_temp_m, aes(x=year, y=decimalLatitude))+
    geom_point(size = 3.5)+
     coord_cartesian(xlim = c(1896, 2022), ylim = c(-35, -20)) + 
    geom_abline(aes(intercept=coef(quantiles_95)[1], slope=coef(quantiles_95)[2], 
                    linetype=qrpv95m$slope_sig), col = "blue", size = 1)+
    geom_abline(aes(intercept=coef(quantiles_05)[1], slope=coef(quantiles_05)[2], 
                    linetype=qrpv05m$slope_sig), col = "blue", size = 1)+
    scale_linetype_manual(values = c("FALSE" = "dashed", "TRUE" = "solid"))+
    labs(x="", y="")+
    theme_classic()+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())+
    theme(legend.position = "none",
          axis.text.x = element_text(size =22),
          axis.text.y = element_text(size =22),
          plot.title = element_text(size=25))
  
  summary(Lat1m, se = "boot")
```
Create quantile latitude regression graph for all mesic species
```{r}
spp = unique(Final_Mesic$Species)

spp_species_plots = list()

for(species in spp) {

  df_temp_m <- Final_Mesic %>% filter(Species == species) #filter DataFrame by your study species

  fit_m <- lm(decimalLatitude ~year, data= df_temp_m)

  quantiles_05 <- rq(fit_m, tau = c(0.05)) %>% summary(se="boot")  #we need to bootstrap for a p-value
  quantiles_95 <- rq(fit_m, tau = c(0.95)) %>% summary(se="boot")

  qrpv05m<-  data.frame(species=species,
                       tau=  quantiles_05[["tau"]],
                       y0= coef(quantiles_05)[1],
                       slope=coef(quantiles_05)[2],
                       slope_pv= coef(quantiles_05)[8],
                       slope_sig = coef(quantiles_05)[8]<0.05)

  qrpv95m<-  data.frame(species=species,
                       tau=  quantiles_95[["tau"]],
                       y0= coef(quantiles_95)[1],
                       slope=coef(quantiles_95)[2],
                       slope_pv= coef(quantiles_95)[8],
                       slope_sig = coef(quantiles_95)[8]<0.05)

  spp_species_plots[[species]] = ggplot(data=df_temp_m,
                                        aes(year, decimalLatitude)) +
    geom_point(size = 3.5)+
    geom_smooth(method = "lm", se = FALSE)+
    coord_cartesian(xlim = c(1895, 2025), ylim = c(-35, -20)) +
    geom_abline(aes(intercept=coef(quantiles_95)[1], slope=coef(quantiles_95)[2],
                    linetype=qrpv95m$slope_sig), col = "blue", size = 1)+
    geom_abline(aes(intercept=coef(quantiles_05)[1], slope=coef(quantiles_05)[2],
                    linetype=qrpv05m$slope_sig), col = "blue", size = 1)+
    scale_linetype_manual(values = c("FALSE" = "dashed", "TRUE" = "solid"))+
    labs(x="", y="")+
    theme_classic()+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())+
    theme(legend.position = "none",
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          plot.title = element_text(size=25))+
    ggtitle(species)

  print(spp_species_plots[[species]])
  
  #ggsave(spp_species_plots[[species]],
        # file=paste0("Lat_mesic_quantreg", species,".png"),
        # width = 15, height = 10, units = "cm", dpi=300)
}
```
Create quantile longitude regression graph for first mesic plant
```{r}
species_list_mesic <- unique(Final_Mesic$Species)

i_m = 1

species_list_mesic[i_m]

df_temp_m <- Final_Mesic %>% filter(Species == species_list_mesic[i_m])

fit_m <- lm(decimalLongitude ~year, data= df_temp_m)

quantiles_05 <- rq(fit_m, tau = c(0.05)) %>% summary(se="boot")

quantiles_95 <- rq(fit_m, tau = c(0.95)) %>% summary(se="boot")

#Create statistics for lower quantile (5th) to plot

qrpv05m<-  data.frame(species=species_list_mesic[i_m], tau=  quantiles_05[["tau"]],
                    y0= coef(quantiles_05)[1],
                    slope=coef(quantiles_05)[2],
                    slope_pv= coef(quantiles_05)[8],
                    slope_sig = coef(quantiles_05)[8]<0.05)

#Create statistics for upper quantile (95th) to plot

qrpv95m<-  data.frame(species=species_list_mesic[i_m], tau=  quantiles_05[["tau"]],
                     y0= coef(quantiles_95)[1],
                     slope=coef(quantiles_95)[2],
                     slope_pv= coef(quantiles_95)[8],
                     slope_sig = coef(quantiles_95)[8]<0.05)

 quant_lon_m <- rbind(qrpv05m, qrpv95m)
```
Create quantile longitude regression graph for all mesic plants
```{r}
quant_lon_m = c()

for (i_m in 1:76) { #loop for species 1 to 40
  
  species_list_mesic[i_m] # check what this species is for funsies
  
  df_temp_m <- Final_Mesic %>% filter(Species == species_list_mesic[i_m]) #filter DataFrame by your study species
  
  fit_m <- lm(decimalLongitude ~year, data= df_temp_m)
  
  quantiles_05 <- rq(fit_m, tau = c(0.05)) %>% summary(se="boot")
  quantiles_95 <- rq(fit_m, tau = c(0.95)) %>% summary(se="boot")
  
  qrpv05m<-  data.frame(species=species_list_mesic[i_m], 
                       tau=  quantiles_05[["tau"]],
                       y0= coef(quantiles_05)[1],
                       slope=coef(quantiles_05)[2],
                       slope_pv= coef(quantiles_05)[8],
                       slope_sig = coef(quantiles_05)[8]<0.05)
  
  qrpv95m<-  data.frame(species=species_list_mesic[i_m], 
                       tau=  quantiles_95[["tau"]],
                       y0= coef(quantiles_95)[1],
                       slope=coef(quantiles_95)[2],
                       slope_pv= coef(quantiles_95)[8],
                       slope_sig = coef(quantiles_95)[8]<0.05)

  quant_prel_m <- bind_rows(qrpv05m, qrpv95m)
  quant_lon_m <- bind_rows(quant_lon_m, quant_prel_m)
}
```
Create quantile longitude regression graph for individual mesic species
```{r}
Lat1m <- filter(Final_Mesic, Species =="Acacia baeuerlenii") %>%
  rq(decimalLongitude ~ year, tau=c(.05,0.95),.)

Lat1dfm<- data.frame(cbind(y=Lat1m[["y"]],
                      x=Lat1m[["x"]][,2],
                        n.05=Lat1m[["fitted.values"]][,1], 
                      n95=Lat1m[["fitted.values"]][,2]))

  ggplot(data=df_temp_m, aes(x=year, y=decimalLongitude))+
    geom_point(size = 3.5)+
     coord_cartesian(xlim = c(1915, 2022), ylim = c(145, 155)) + 
    geom_abline(aes(intercept=coef(quantiles_95)[1], slope=coef(quantiles_95)[2], 
                    linetype=qrpv95m$slope_sig), col = "blue", size = 1)+
    geom_abline(aes(intercept=coef(quantiles_05)[1], slope=coef(quantiles_05)[2], 
                    linetype=qrpv05m$slope_sig), col = "blue", size = 1)+
    scale_linetype_manual(values = c("FALSE" = "dashed", "TRUE" = "solid"))+
    labs(x="", y="")+
    theme_classic()+
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank())+
    theme(legend.position = "none",
          axis.text.x = element_text(size =22),
          axis.text.y = element_text(size =22),
          plot.title = element_text(size=25))+
    ggtitle(species)
  
    print(spp_species_plots[[species]])
  
  ggsave(spp_species_plots[[species]],
         file=paste0("Lon_Mesic_quantreg", species,".png"),
         width = 20, height = 15, units = "cm", dpi=300)
  
  summary(Lat1m, se = "boot")
```
Create quantile longitude regression graph for all mesic species
```{r}
spp = unique(Final_Mesic$Species)

spp_species_plots = list()

for(species in spp) {

  df_temp_m <- Final_Mesic %>% filter(Species == species) #filter DataFrame by your study species

  fit_m <- lm(decimalLongitude ~year, data= df_temp_m)

  quantiles_05 <- rq(fit_m, tau = c(0.05)) %>% summary(se="boot")  #we need to bootstrap for a p-value
  quantiles_95 <- rq(fit_m, tau = c(0.95)) %>% summary(se="boot")

  qrpv05m<-  data.frame(species=species,
                       tau=  quantiles_05[["tau"]],
                       y0= coef(quantiles_05)[1],
                       slope=coef(quantiles_05)[2],
                       slope_pv= coef(quantiles_05)[8],
                       slope_sig = coef(quantiles_05)[8]<0.05)

  qrpv95m<-  data.frame(species=species,
                       tau=  quantiles_95[["tau"]],
                       y0= coef(quantiles_95)[1],
                       slope=coef(quantiles_95)[2],
                       slope_pv= coef(quantiles_95)[8],
                       slope_sig = coef(quantiles_95)[8]<0.05)

  spp_species_plots[[species]] = ggplot(data=df_temp_m,
                                        aes(year, decimalLongitude)) +
    geom_point(size = 3.5)+
    geom_smooth(method = "lm", se = FALSE)+
    coord_cartesian(xlim = c(1895, 2025), ylim = c(145, 155)) +
    geom_abline(aes(intercept=coef(quantiles_95)[1], slope=coef(quantiles_95)[2],
                    linetype=qrpv95m$slope_sig), col = "blue", size = 1)+
    geom_abline(aes(intercept=coef(quantiles_05)[1], slope=coef(quantiles_05)[2],
                    linetype=qrpv05m$slope_sig), col = "blue", size = 1)+
    scale_linetype_manual(values = c("FALSE" = "dashed", "TRUE" = "solid"))+
    labs(x="", y="")+
    theme_classic()+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())+
    theme(legend.position = "none",
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          plot.title = element_text(size=25))+
    ggtitle(species)

  print(spp_species_plots[[species]])
  
  ggsave(spp_species_plots[[species]],
         file=paste0("Lon_mesic_quantreg", species,".png"),
         width = 20, height = 15, units = "cm", dpi=300)
}
```